---
title: "aelab"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{instruction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
rmarkdown.html_vignette.check_title = FALSE
```


# Installation

Install `aelab` package from Github. `devtools` need to be install though `install.packges("devtools")`.

```{r}
library(aelab)
```

Load other required packages. Install through `install.packages("package_name")` if not already installed.

```{r}
library(readxl)
library(tibble)
library(lubridate)
library(stats)
library(dplyr)
library(openxlsx)
```

# Load and process data from LI-COR

Unnecessary rows and columns are removed. NaN values of GHG data are removed.

```{r}
ghg_data_path <- system.file("extdata", "ch4.xlsx", package = "aelab", mustWork = T)
ch4 <- tidy_licor(ghg_data_path, "ch4")
ch4[c(1:5), ]
```

# Convert LI-COR time

Convert the time in LI-COR to match the time in real life (if there are any differences).

```{r}
ch4 <- convert_time(ch4, min = -15, sec = 30)
ch4[c(1:5), ]
```

# Calculate the slope based on the measurement start time

## Method 1: Load from excel

Type the date and time of GHG flux measurement (start time) in excel, then load the file into R.

```{r}
ref_data_path <- system.file("extdata", "reference.xlsx", package = "aelab", mustWork = T)
ref <- read_excel(ref_data_path)
ref
```

Calculation of the slope of methane concentration over time using the `date_time` value in the `ref` data. In the results, `start_time` and `end_time` are the time range of the data used to perform regression. `slope` is the slope and `R-square` is the R^2 of the regression. `reference_time` is the start time of the measurement from the input.

```{r}
calculate_regression(ch4, ghg = "CH4", reference_time = ref$date_time)
```

The default duration of measurement is set to `7` minutes, and the number of rows selected to perform regression is `300`. You can modify these values if desired using the input variables `duration_minutes` and `num_rows` according to your needs.
```{r}
calculate_regression(ch4, ghg = "CH4", reference_time = ref$date_time,
                     duration_minutes = 5, num_rows = 300)
```

## Method 2: Type from R

The start time of measurement can also be input directly into the function. Note that `as.POSIXct()` is necessary.

```{r}
calculate_regression(ch4, ghg = "CH4", reference_time = as.POSIXct("2023-03-11 07:32:00", tz = "UTC"))
```
